---
author: Lucas Veras
date: "`r Sys.Date()`"
output:
  pdf_document:
    includes:
      in_header: columns.tex
header-includes:
   - \usepackage{fullpage}
   - \usepackage{sourcesanspro}
   - \usepackage{sectsty}
   - \usepackage{fontawesome5}
   - \usepackage{hyperref}
   - \definecolor{dark-gray}{RGB}{68, 68, 68}
   - \definecolor{light-gray}{gray}{0.35}
   - \usepackage{fancyhdr}
   - \usepackage{lastpage}
   - \pagestyle{fancy}
   - \cfoot{\thepage\ / \pageref{LastPage}}
   - \renewcommand{\headrulewidth}{0pt}
---

```{r, include = FALSE}
knitr::opts_chunk$set(results = "asis", echo = FALSE)

source("cv_printing_functions.R")

# Read in all data and initialize a CV printer object
cv <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1lmTkQPjWL7ZVcTD2nIzMpnMSFe14XAe-Njb3PN3smcQ/edit#gid=917338460",
  pdf_mode = "true"
)

```

\begin{tabular*}{\textwidth}{@{}p{.45\textwidth}@{\extracolsep{\fill}}r@{}}
\raggedright
\begin{LARGE}
\textbf{Lucas Veras} \\
\end{LARGE}
\vspace{2.5em}
\begin{Large}
\textbf{\textit{Curriculum Vitae}}
\end{Large}
&
\begin{tabular}[t]{ r@{}}
```{r echo = FALSE, results = 'asis'}
contact_info <- print_contact_info(cv)
cat(contact_info)
```
\end{tabular}
\end{tabular*}

\rule{\linewidth}{0.8pt}

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{graduation-cap}} \textbf{Education}
\end{Large}

```{r}
edu <- print_education(cv)
cat(edu)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{award}} \textbf{Awards}
\end{Large}

```{r}
awards <- print_awards(cv)
cat(awards)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{file-alt}} \textbf{Papers}
\end{Large}

```{r}
papers <- print_papers(cv)
cat(papers)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{book}} \textbf{Book chapters}
\end{Large}

```{r}
books <- print_books(cv)
cat(books)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{chalkboard}} \textbf{Conference publications}
\end{Large}

```{r}
conference <- print_conference(cv)
cat(conference)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{file-signature}} \textbf{Reviews for journals}
\end{Large}

```{r}
review <- print_review(cv)
cat(review)
```

\vspace*{\fill}
\flushright \footnotesize Last updated on `r Sys.Date()`
