---
author: Lucas Veras
date: "`r Sys.Date()`"
output:
  pdf_document:
    includes:
      in_header: columns.tex
header-includes:
   - \usepackage{fullpage}
   - \usepackage{sourcesanspro}
   - \usepackage{sectsty}
   - \usepackage{fontawesome5}
   - \usepackage{hyperref}
   - \definecolor{dark-gray}{RGB}{68, 68, 68}
   - \definecolor{light-gray}{gray}{0.35}
   - \usepackage{fancyhdr}
   - \usepackage{lastpage}
   - \pagestyle{fancy}
   - \cfoot{\thepage\ / \pageref{LastPage}}
   - \renewcommand{\headrulewidth}{0pt}
---

```{r, include = FALSE}
knitr::opts_chunk$set(results = "asis", echo = FALSE)

source("cv_printing_functions.R")

# Read in all data and initialize a CV printer object
cv <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1muaB2KmoQj_OvOB54AJcTvLJ_sJGdHXOZs1c3tGyB5A/edit#gid=1730172225",
  pdf_mode = "true"
)

```

\begin{tabular*}{\textwidth}{@{}p{.45\textwidth}@{\extracolsep{\fill}}r@{}}
\raggedright
\begin{LARGE}
\textbf{Lucas Veras} \\
\end{LARGE}
\vspace{3.5em}
\begin{Large}
\textbf{\textit{Curriculum Vitae}}
\end{Large}
&
\begin{tabular}[t]{ r@{}}
```{r echo = FALSE, results = 'asis'}
contact_info <- print_contact_info(cv)
cat(contact_info)
```
\end{tabular}
\end{tabular*}

\rule{\linewidth}{0.8pt}

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{user}} \textbf{Summary}
\end{Large}

```{r}
sum <- print_summary(cv)
cat(sum)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{code}} \textbf{Technical skills}
\end{Large}

```{r}
skl <- print_skills(cv)
cat(skl)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{user-tie}} \textbf{Professional experience}
\end{Large}

```{r}
exp <- print_experience(cv)
cat(exp)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{book}} \textbf{Courses}
\end{Large}

```{r}
cou <- print_courses(cv)
cat(cou)
```

\vspace{1.5em}

\pagebreak

\begin{Large}
\textcolor{dark-gray}{\faIcon{graduation-cap}} \textbf{Education}
\end{Large}

```{r}
edu <- print_education(cv)
cat(edu)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{comment}} \textbf{Languages}
\end{Large}

```{r}
lan <- print_languages(cv)
cat(lan)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{award}} \textbf{Awards}
\end{Large}

```{r}
awards <- print_awards(cv)
cat(awards)
```

\vspace{1.5em}

\begin{Large}
\textcolor{dark-gray}{\faIcon{file-alt}} \textbf{Scientific papers}
\end{Large}

```{r}
papers <- print_papers(cv)
cat(papers)
```

\vspace*{\fill}
\flushright \footnotesize Last updated on `r Sys.Date()`

\flushright \footnotesize The source code of this CV is available on \textcolor{light-gray}{\href{https://github.com/verasls/verasls.github.io/tree/master/CV}{GitHub \faIcon{github}}}
